Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-08 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
a bit of work on methods

*Data collection and preparation*
The SCBI ForestGEO plot was censused in 2008, 2013, and 2018 following standard ForestGEO protocols, whereby all free-standing woody stems >= 1cm diameter at breast height (DBH) were mapped, tagged, measured at DBH, and identified to species [@condit_tropical_1998]. From this census data, we used measurements of DBH from 2008 to calculate historical DBH (described below), along with tree location in the plot to determine the topographic wetness index. *I think that's it, really, in terms of data we're using coming from the censuses.*

We analyzed tree-ring data from the twelve species contributing most to woody aboveground net primary productivity (ANPP), which together comprised 97% of study plot ANPP between 2008 and 2013 [@helcoski_growing_2019]. Cores were obtained in 2010-2011 or 2016-2017 from a breast height of 1.3m using a 5mm increment borer. In 2010-2011, cores were collected from randomly selected live trees were selected at random from each species, with at least 30 of those trees having a diameter at breast height (DBH) of at least 10cm [@bourg_initial_2013]. In 2016-2017, cores were collected from all dead trees found in the annual mortality census [@gonzalezakre_patterns_2016]. Cores were sanded, measured, and cross-dated using standard procedures, as detailed in [@helcoski_growing_2019]. The resulting chronologies have been [published](https://github.com/SCBI-ForestGEO/climate_sensitivity_cores) in association with @helcoski_growing_2019: (ITRDB). *is this a database?*

>>>>

*Data collection and preparation*
The SCBI ForestGEO plot was censused in 2008, 2013, and 2018 following standard ForestGEO protocols, whereby all free-standing woody stems >= 1cm diameter at breast height (DBH) were mapped, tagged, measured at DBH, and identified to species [@condit_tropical_1998]. From this census data, we used measurements of DBH from 2008 to calculate historical DBH (described below), along with tree location in the plot to determine the topographic wetness index. Furthermore, we used data for all stems >= 10cm to analyze functional trait composition relative to tree height.  *I added the last sentence-- not sure if you've described that below yet. I don't think you need to note here which data we use, so long as that's described in the portions where you describe the analysis.*

We analyzed tree-ring data from the twelve species contributing most to woody aboveground net primary productivity (ANPP), which together comprised 97% of study plot ANPP between 2008 and 2013 [@helcoski_growing_2019]. Cores were obtained in 2010-2011 or 2016-2017 from a breast height of 1.3m using a 5mm increment borer. In 2010-2011, cores were collected from randomly selected live trees of species with at least 30 individuals of DBH >= 10cm [@bourg_initial_2013]. In 2016-2017, cores were collected from all trees found dead in the annual mortality census [@gonzalezakre_patterns_2016]. Cores were sanded, measured, and cross-dated using standard procedures, as detailed in [@helcoski_growing_2019]. The resulting chronologies have been published in association with @helcoski_growing_2019: (ITRDB; GitHub/Zenodo). *is this a database? Yes. Ryan submitted the data but I don't think its posted yet. We should also cite GitHub/Zenodo here. I'll come back to that. *
